Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-09 article.tex
fix the citation

\section{Methodology}
\section{Signal filtering} \label{sec:filter}
% Explain why we need to filter
% TODO

\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus "motivée"}

@@

% introduce the notion of dependence / independence
From a probabilistic point of view, the inference of the undirected network
can be formulated as inferring conditional dependences and
independences.  Even if \textit{independence
does no imply causation}[todo cite], it gives insight on the underlying connectivity
network. For instance, the graph $A \rightarrow B \rightarrow C$ translates the
following dependances and independances: $A \not\perp B$, $A \not\perp B | C$,
$B \not\perp C$, $B \not\perp C | A$, but $A \perp C | B$ and  $A \not\perp C$.

>>>>

\section{Signal filtering} \label{sec:filter}
% Explain why we need to filter
% TODO

\textcolor{red}{AS: Après avoir discuté avec Gilles, une autre façon de présenter les choses qui est moins rigoureuse que l'approche de AJ mais plus "motivée"}
Prior inferring the network, the fluorescent calcium time series are smoothed
using several linear and non linear filters.

@@

% introduce the notion of dependence / independence
From a probabilistic point of view, the inference of the undirected network
can be formulated as inferring conditional dependences and
independences.  Even if \textit{correlation
does no imply causation}[todo cite], it gives insight on the underlying connectivity
network. For instance, the graph $A \rightarrow B \rightarrow C$ translates the
following dependances and independances: $A \not\perp B$, $A \not\perp B | C$,
$B \not\perp C$, $B \not\perp C | A$, but $A \perp C | B$ and  $A \not\perp C$.
